%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Sina}}}}} % First name
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Kamali}}}}} % Last name
	
	\vspace{6pt}
	
	{\huge Indie Game Developer} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{MapMarker}{12}{Tehran/Iran}\\
	\icon{Phone}{12}{+98 912 393 5925}\\
	\icon{At}{12}{\href{mailto:sininoir@gmail.com}{sininoir@gmail.com}}\\	
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{Linkedin}{12}{\href{https://linkedin.com/in/CnaKamali}{Sina Kamali}}\\
	\icon{Github}{12}{\href{https://github.com/PapaSinku}{github.com/PapaSinku}}\\
	% \icon{Twitter}{12}{\href{https://twitter.com/@alyxvance}{@alyxvance}}\\
\end{minipage}

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\cvsect{About Me}

\begin{minipage}[t]{0.4\textwidth} % 40% of the page width for the introduction text
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	I am a young developer from Iran. I am a great debugger and love programming, game development and solving all kinds of problems. In my opinion solving the problems around us using the knowledge we 
	have acquired in life, is the ultimate goal that a person can follow, no matter how big or small the solved problems are.
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.5\textwidth} % 50% of the page for the skills bar chart
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\begin{barchart}{5.5}
		\baritem{C}{70}
		\baritem{C++}{85}
		\baritem{Java}{70}
		\baritem{Python}{100}
		\baritem{Javascript}{65}
		\baritem{C\#}{75}
		\baritem{Git}{80}
		\baritem{LaTeX}{65}
		\baritem{Linux}{85}
	\end{barchart}
\end{minipage}

\begin{center}
	\bubbles{6/git, 4/Office, 6/Debugging, 3/Unity, 5/UnrealEngine}
\end{center}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
	\entry
		{10/2019 -- 9/2020}
		{Lead Developer}
		{Hamim Co.}
		{Developed a framework for predicting and trading in the crypto-currency market. It used a real-time Reinforcement learning algorithm alongside with typical technical analysis. The project was developed with Python in a group of 5.\\ \texttt{Python}\slashsep\texttt{ML}\slashsep\texttt{Trading}\slashsep\texttt{Linux}}
	\entry
		{7/2019 -- 10/2019\\\footnotesize{part time}}
		{Programmer \& Data Scientist}
		{University of Tehran}
		{Worked on a Fraud Detection agent used for detecting fake clicks on ads. Our final solution got an accuracy of 85\% on the official Kaggle test data. The project was written in Python. \\ \texttt{Python}\slashsep\texttt{ML}\slashsep\texttt{Data Science}\slashsep\texttt{Linux} }
	\entry
		{2/2020 -- On Going\\\footnotesize{part time}}
		{Teaching Assistant of The Discrete Mathematics Course}
		{University of Tehran}
		{Working as a TA in the discrete mathematics course. My responsibilities involve designing problems, quizes and grading them.    \\ \texttt{Teaching Assistant}\slashsep\texttt{Latex}\slashsep\texttt{Discreet Mathematics}}
	\entry
		{9/2020 -- On Going\\\footnotesize{part time}}
		{Teaching Assistant of The Data Structure Course}
		{University of Tehran}
		{Working as a TA in the Data Structure course. My responsibilities involve designing problems, quizes, projects and grading them.    \\ \texttt{Teaching Assistant}\slashsep\texttt{Python}\slashsep\texttt{Data Structure}}
	\entry
		{2/2021 -- On Going\\\footnotesize{part time}}
		{Teaching Assistant of The Artificial Intelligence Course}
		{University of Tehran}
		{Working as a TA in the artificial intelligence course. My responsibilities involve designing problems, quizes and grading them.    \\ \texttt{Teaching Assistant}\slashsep\texttt{Python}\slashsep\texttt{Pandas}\slashsep\texttt{Artificial Intelligence}}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
	\entry
		{2018 -- On Going}
		{Bachelor's Degree}
		{University of Tehran}
		{Studying to get a Bachelor's Degree on Computer Engineering.}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	Projects
%----------------------------------------------------------------------------------------

\cvsect{Projects}

\begin{entrylist}
	\entry
		{2021}
		{Sins \& Virtues}
		{Independent}
		{A Text-Based game built from the ground up by myself using Python. The game is a modern take on old Text-Based RPGs with some fun new mechanics like a day-night cycle, an upgrade system and many more. This project is available on my personal git.\\ \texttt{Python}\slashsep\texttt{C++}\slashsep\texttt{Game Development}\slashsep\texttt{Linux}}
	\entry
		{2020}
		{Meriq}
		{Independent}
		{A 3D Top-Down shooter made by myself using Unreal Engine Blueprints. The game offers many fun gameplay elements like an upgrade system and a dynamic difficulty adjustment system to tune your game to the way you like to play. This project is ready and has a Shipment build but has not been released yet.\\ \texttt{C++}\slashsep\texttt{Blueprints}\slashsep\texttt{Game Development}\slashsep\texttt{Unreal Engine}}
	\entry
		{2020}
		{Discrete Mathematics Contest Bot(DMC Bot)}
		{DM course at University of Tehran}
		{A mail bot developed by me and some other friends for holding the DM Contest in the global pandemic of 2020. The project was developed with Python.\\ \texttt{Python}\slashsep\texttt{Mail Bot}\slashsep\texttt{Discrete Mathematics}}
	\entry
		{2019}
		{Color Switch Replica}
		{Independent}
		{A smartphone game similar to Color Switch Developed using C\# and the Unity Engine by myself. The game had some fun features like a shop where you could buy upgrades for your character.\\ \texttt{C\#}\slashsep\texttt{Unity Engine}\slashsep\texttt{Game Development}}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Languages}
	
	\textbf{Persian} - native\\
	\textbf{English} - proficient\\
	\textbf{Arabic}  - rudimentary
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Hobbies}
	
	I love gaming, programming, watching movies and series and doing adrenaline filled activities.
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Non profit}
	
	I have developed several Open Source projects to help others on my github account.
\end{minipage}

%----------------------------------------------------------------------------------------

\end{document}
