%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Notable Academic Projects}


%-------------------------------------------------------------------------------
%	CONTENT


\begin{cventries}

%---------------------------------------------------------
  \cventry
    {A smart contract made using Solidity} % Degree
    { \href{https://github.com/kamali-sina/Smart-Debt-Handler}{Smart Debt Handler} } % Institution
    {Cryptocurrency} % Location
    {} % Date(s)
    {
       A smart debt handler similar to Splitwise, which tracks users' debts and updates them based on the loops users create between each other.
    }

    \cventry
    {An Address maker made using pure Python} % Degree
    { \href{https://github.com/kamali-sina/BTC-Address-Maker}{BTC Address Maker} } % Institution
    {Cryptocurrency} % Location
    {} % Date(s)
    {
      This project was developed to further understand the math and explicit details of creating a key pair. This project can make any kind of famous key pairs in either the test net or the main net.
    }

    \cventry
    {A fully functioning FTP server} % Degree
    { \href{https://github.com/kamali-sina/FTP-server}{FTP Server} } % Institution
    {Computer Networks} % Location
    {} % Date(s)
    {
      A fully functioning FTP server with many capabilities implemented in C++ that uses socket programming to communicate with clients at a low level.
    }

    \cventry
    {A fully functioning IMDB clone} % Degree
    { \href{https://github.com/kamali-sina/iemdb}{IEMDB} } % Institution
    {Internet Engineering} % Location
    {} % Date(s)
    {
      A complete implementation of a website from scratch by me and my teammate. This project was developed using Java and Spring for the \href{https://github.com/kamali-sina/iemdb}{back-end}, and React for its \href{https://github.com/kamali-sina/iemdb-frontend}{front-end}. We have used tools like CI/CD pipelines, JDBC, JUnit, Github Oauth apps, etc.
    }

    \cventry
    {A simulation of network functions} % Degree
    { \href{https://github.com/kamali-sina/Network-Function-Simulation}{Network Function Simulation} } % Institution
    {Computer Networks} % Location
    {} % Date(s)
    {
      A complete simulation of network functions created using C++. It supports various network components and uses multi-threading to run the simulations simultaneously.
    }

    \cventry
    {A multi-threaded C program that predicts prices based on trained regression data} % Degree
    { \href{https://github.com/kamali-sina/Multi-Threaded-Prediction}{Multi-Threaded Prediction} } % Institution
    {Computer Networks} % Location
    {} % Date(s)
    {
      This project was created to toy with multi-threading concepts and to get more familiar with them.
    }

    

%---------------------------------------------------------
\end{cventries}
